The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources

### 2020-04-04 paper.tex
One last tiny edit before sending to Andreas.

\subsubsection{Phase-space diffusion} \label{psd}
Much of this subsection was borrowed from \citet{2017MNRAS.467.4180S}, Section E1, which made use the same modified version of \textsc{AR-Chain}.

>>>>

\subsubsection{Phase-space diffusion} \label{psd}
Much of this subsection was borrowed from \citet{2017MNRAS.467.4180S}, Section E1, which made use of the same modified version of \textsc{AR-Chain}.
